Abstractions and exemplars: the measure noun phrase alternation in German

### 2018-04-08 Latex/sections/3corpus.tex
Minor corrections.
First round of shortening.

For the present study, I used the German \textit{Corpus from the Web} (COW) in its 2014 version DECOW14A (\citealp{SchaeferBildhauer2012full}, and \citealp{Schaefer2015b}, as well as \citealp{BiemannEa2013}, and \citealp{SchaeferBildhauer2013}, for overviews of web corpora in general and the methodology of their construction), which contains almost 21 billion tokens.%
\footnote{The COW corpora (Dutch, English, French, German, Spanish, Swedish) are made available for free at \url{https://www.webcorpora.org}.
At the time of this writing, a newer 2016 version DECOW16A has already been released.}
I chose this corpus for two main reasons.%
\footnote{The use of web data for linguistic research does require explicit and careful justification.
Due to the noisy nature and unknown composition of the web, only carefully designed and established web corpora like the COW corpora or the SketchEngine corpora \citep{KilgarriffEa2014} should be used.
Clearly, using search engine results is ``bad science'' for many reasons, most prominently total non-replicability of results, as \cite{Kilgarriff2006} pointed out more than ten years ago.
Careless use of search engine results is still found, however, see for example \citet[171--175]{DeclerckBrems2016}.}
First, the external validity of any study is increased through a higher heterogeneity of the sample \citep[30]{MaxwellDelaney2004}, and the DECOW14A corpus has clearly a much more heterogeneous composition compared to the only other very large corpus of German, the DeReKo \citep{KupietzEa2010} of the Institute for the German Language (IDS), which contains almost exclusively newspaper texts.%
\footnote{It was shown in \cite{W16-2601} that, for example, the range of topics covered is much smaller in DeReKo compared to DECOW14A.}
Second, it was already mentioned that normative grammars often adopt clear positions regarding the grammaticality of either the \NACa\ or the \PGCa.
Thus, newspaper text or any other text that conforms strongly to normative grammars might not represent the alternation phenomenon fully (and without bias) because authors and proofreaders who must adhere to normative guidelines might favour one alternative or the other explicitly.
Web corpora, on the other hand, contain at least some amount of non-standard language from forums and similar sources.
For these or similar reasons, COW corpora have been used in a number of peer-reviewed publications, for example \cite{VanGoethemHiligsmann2014}, \cite{VanGoethemHuening2015}, \cite{MuellerS2014}, \cite{Schaefer2016c}, \cite{SchaeferSayatz2014}, \cite{SchaeferSayatz2016}, and \cite{Zimmer2015}. 
Therefore, DECOW14A is a valid choice for this study.

@@

\begin{table}
  \centering
  \begin{tabular}{llll}
    Unit of reference & Variable                      & Type    & Levels (for factors only) \\
    \midrule
    Document       & Badness                          & numeric &                           \\
                   & Genitives                        & numeric &                           \\
    Sentence       & Cardinal                         & factor  & Yes, No                   \\
                   & \textbf{Construction (response)} & factor  & NACadj, PGCadj            \\
                   & Measurecase                      & factor  & Nom, Acc, Dat             \\
    Kind lemma     & Kindattraction                   & numeric &                           \\
                   & (Kindcollo)                      & numeric &                           \\
                   & Kindfreq                         & numeric &                           \\
		   & Kindgender                       & factor  & Masc, Neut, Fem             \\
    Measure lemma  & Measureattraction                & numeric &                           \\
                   & (Measurecollo)                   & numeric &                           \\
                   & Measureclass                     & factor  & Physical, Container,      \\
                   &                                  &         & Amount, Portion, Rest     \\
                   & Measurefreq                      & numeric &                           \\
  \end{tabular}
  \caption{Annotated variables for the main study}
  \label{tab:variables}
\end{table}

@@

To capture the influence of style mentioned in Section~\ref{sec:analyses}, two proxy variables were used.
At the document level, the DECOW14A corpus has an annotation for \textit{Badness}.
As described in \cite{SchaeferEa2013}, \textit{Badness} measures how well the distribution of highly frequent short words in the document matches a pre-generated language model for German.
They also show that the Badness score corresponds robustly with human raters' intuitions about text coherence and text quality (see the paper for an operationalisation of this notion).
Documents with higher Badness usually contain more incoherent language, shorter sentences, etc.
If the \PGCa\ actually favours more elaborate stylistic levels, a high \textit{Badness} should be correlated with fewer occurrences.
Documents in DECOW14 have also been annotated with a variable called \textit{Genitives}.
The higher the values of this variable, the lower the proportion of genitives among all case-bearing forms is.
A high number of genitives is also indicative of a more formal, elaborate style close to the written standard.
However, the use of this variable as a regressor in the present study might be considered problematic.
Since the \PGCa\ contains a genitive itself, the regressor variable \textit{Genitive} and the document-level variable \textit{Genitives} are not fully independent.
Since instances of the \PGCa\ make up for only a minute fraction of all genitives, however, I still use \textit{Genitives} as a regressor.%
\footnote{A reviewer suggested that a fully fledged multidimensional analysis \citep{Biber1988} would help to improve the operationalisation of the influence of style.
This sounds plausible, but there simply is no large corpus of German for which similar data have been published.
In the meantime, the creators of COW and the Institut für Deutsche Sprache (IDS) Mannheim have developed a similar annotation framework (COReX), and the COW creators have pre-released a non-public beta version of the corresponding data base for DECOW16A to their users.
This data base contains 118 automatically extracted lexico-grammatical features for each document.
However, at this time, it is not recommended for use in published research.
Also, the genitive is generally considered a good indicator of style in German, and its frequency is usually high enough such that the \textit{Genitives} score is a stable measure even for shorter documents (compared to first or second person pronouns, for example, which are totally absent in a majority of documents).
The genitive is still the dominant attributive case in German.}

@@

The coefficient estimates are specified in Table~\ref{tab:smalltable} for each regressor (or regressor level) in the columns labelled \textit{Coefficient}.
Given the coding of the response variable, coefficients leaning to the positive side can be interpreted as characterising a configuration typical of the \PGCd.
For a robust quantification of the precision of the estimation, I ran a parametric bootstrap (using the \mbox{\textit{confint.merMod}} function from \textit{lme4}) with 1,000 replications and using the percentile method for the calculation of the intervals.
The resulting 95\% bootstrap confidence intervals are reported in Table~\ref{tab:smalltable} in the columns labelled \textit{CI low} and \textit{CI high} (= upper and lower 2.5th percentiles).
The column \textit{CI excludes 0} shows an asterisk for those intervals that do not include 0.
Furthermore, for each regressor, a p-value was obtained by dropping the regressor from the full model, re-estimating the nested model, and comparing it to the full model.
Instead of inexact Wald approximations and Likelihood Ratio Tests, I used a drop-in bootstrap replacement for the Likelihood Ratio Test in the form of the function \textit{PBmodcomp} from the \textit{pbkrtest} package \citep{HalekohHojsgaard2014}.
I call the corresponding value $p_{\text{PB}}$, and it is given in the respective columns in Table~\ref{tab:smalltable}.
Regressors which did not reach sig=0.05 in in the PBmodcomp test (\textit{Kindfreq}, \textit{Kindgender}, and \textit{Measurefreq}) were removed from the model, appear in brackets in Table~\ref{tab:smalltable}, and consequently have no coefficient estimates.%
\footnote{My approach to statistical inference is essentially Fisherian \citep{Fisher1935,Fisher1959}, and hence I use the term \textit{sig level} instead of the term \textit{$\alpha$ level} known from null hypothesis significance testing (NHST).
For overviews of systems of statistical inference with special focus on this and related questions, see \citet{Lehmann1993,Lehmann2011} or the shorter \citet{Perezgonzalez2015}.}
The overall intercept is -5.370 and reoresents \textit{Cardinal=Yes}, \textit{Measureclass=Physical} and 0 for all (z-transformed) numeric regressors.
The standard deviation in the random intercepts is 1.157 for \textit{Measurelemma} ($p_{\text{PB}}=0.001$) and 0.923 for \textit{Kindlemma} ($p_{\text{PB}}=0.002$).
Nakagawa \& Schielzeth's pseudo-coefficient of determination is $R_m^2=0.278$ and $R^2_c=0.566$ (see \citealp{Gries2015} for a basic introduction to these $R^2$ measures, or else \citealp{NakagawaSchielzeth2013}).

@@

For the main study, each of the 2,365 noun–noun combinations was queried in the alternating constructions \PGCa\ and \NACa\ in DECOW14A.%
\footnote{Due to processing considerations with the COW interface at the time, only ten slices of DECOW14A were used, which add up to approximately 10 billion tokens.}
For the manual annotation process, a random sub-sample was generated.
For each mass noun, the concordance was downsampled randomly to maximally 100 sentences, which resulted in 6,843 sentences without further downsampling.
In the manual annotation process the size was further reduced to 5,063 sentences due to removal of noisy material, erroneous hits, and uninformative cases where the measure noun was in the genitive, in which case the \NACa\ cannot be distinguished from the \PGCa.
Given the careful sampling procedure described in this section and Section~\ref{sec:bootstrappinlemmapairs}, we can be highly certain that it contains all relevant and reasonably frequent noun–noun combinations in the target constructions.%
\footnote{In a similar fashion, the 100 most frequent measure nouns occurring with plural kind nouns were listed and queried, resulting in a sample of 871 sentences.
As stated in Section~\ref{sec:germanmeasurenps}, the \NACa\ is virtually never used with plural kind nouns, and this sample was not used except for quantifying the frequency of occurrence of the constructions (67 times \NACa\ and 794 times \PGCa).
The sample is distributed with the data package accompanying this paper.}

@@

Standard diagnostics show that the model quality is quite good.%
\footnote{Notice that no aggressive model selection was applied, especially not upward model selection including probing for interactions.
I am convinced that models should be specified based on theoretical considerations (including known nuisance effects) to avoid the dangers of data dredging and to avoid models which are difficult to interpret.
Removal of useless regressors (judging by, for example, the PBmodcomp test and coefficients of determination) is the only type of model selection I allow in my research.}
Nakagawa \& Schielzeth's pseudo-coefficient of determination is $R_m^2=0.409$ and $R^2_c=0.495$.
The rate of correct predictions is 0.843, which means a proportional reduction of error of $\lambda=0.297$.
Generalised variance inflation factors for the regressors were calculated to check for multicollinearity \citep{FoxMonette1992,ZuurEa2010}, and the highest corrected $\text{GVIF}^{1/2\text{df}}$ was 1.520 for \textit{Cardinal}.
The lemma intercepts have standard deviations of $\sigma_{\text{Measurelemma}}=0.448$ and $\sigma_{\text{Kindlemma}}=0.604$.
Only \textit{Kindfreq} ($\mpPB=0.095$) could be seen as slightly too high to be convincing, failing at sig=0.05.

@@

The results reported in Section~\ref{sec:corpushierarchicalmodel} generally confirm the hypotheses from Section~\ref{sec:analyses}.
First, the prototypicality effect related to the non-alternating \PGCd\ and \NACb\ can be shown (see the effect plots in Figure~\ref{fig:eff:attraction}).%
\footnote{Effect plots were created using the \textit{effects} package \citep{Fox2003}.
They show the changes in probability for the outcome (y-axis) dependent on values of a regressor (x-axis) at typical values of all other regressors.
The vertical bars (categorical variables), and the grey areas (continuous variables) are asymptotic 95\% confidence intervals calculated from \textit{glmer}.
They are not bootstrapped.
Readers should be aware that the axes are specifically scaled so as to result in a linear plot, and that the range of the axes varies between plots.}
The effect is as expected:
if a lemma appears relatively more often in the \PGCd\ (compared to its frequency in the \NACb), the \PGCa\ tends to be chosen over the \NACa\ with this specific lemma.
The effect for measure nouns is stronger, and it was estimated with higher precision.

>>>>

For the present study, I used the German \textit{Corpus from the Web} (COW) in its 2014 version DECOW14A (\citealp{SchaeferBildhauer2012full}, and \citealp{Schaefer2015b}, as well as \citealp{BiemannEa2013}, and \citealp{SchaeferBildhauer2013}, for overviews of web corpora in general and the methodology of their construction), which contains almost 21 billion tokens.%
\footnote{The COW corpora (Dutch, English, French, German, Spanish, Swedish) are made available for free at \url{https://www.webcorpora.org}.
At the time of this writing, a newer 2016 version DECOW16A has already been released.}
I chose this corpus for two main reasons.
First, the external validity of any study is increased through a higher heterogeneity of the sample \citep[30]{MaxwellDelaney2004}, and the DECOW14A corpus has clearly a much more heterogeneous composition compared to the only other very large corpus of German, the DeReKo \citep{KupietzEa2010} of the Institute for the German Language (IDS), which contains almost exclusively newspaper texts.%
\footnote{It was shown in \cite{W16-2601} that, for example, the range of topics covered is much smaller in DeReKo compared to DECOW14A.}
Second, it was already mentioned that normative grammars often adopt clear positions regarding the grammaticality of either the \NACa\ or the \PGCa.
Thus, newspaper text or any other text that conforms strongly to normative grammars might not represent the alternation phenomenon fully (and without bias) because authors and proofreaders who must adhere to normative guidelines might favour one alternative or the other explicitly.
Web corpora, on the other hand, contain at least some amount of non-standard language from forums and similar sources.
For these or similar reasons, COW corpora have been used in a number of peer-reviewed publications, for example \cite{VanGoethemHiligsmann2014}, \cite{VanGoethemHuening2015}, \cite{MuellerS2014}, \cite{Schaefer2016c}, \cite{SchaeferSayatz2014}, \cite{SchaeferSayatz2016}, and \cite{Zimmer2015}. 
Therefore, DECOW14A is a valid choice for this study.

@@

\begin{table}
  \centering
  \begin{tabular}{llll}
    Unit of reference & Variable                      & Type    & Levels (for factors only) \\
    \midrule
    Document       & Badness                          & numeric &                           \\
                   & Genitives                        & numeric &                           \\
    Sentence       & Cardinal                         & factor  & Yes, No                   \\
                   & \textbf{Construction (response)} & factor  & NACadj, PGCadj            \\
                   & Measurecase                      & factor  & Nom, Acc, Dat             \\
    Kind lemma     & Kindattraction                   & numeric &                           \\
                   & (Kindcollo)                      & numeric &                           \\
                   & Kindfreq                         & numeric &                           \\
		   & Kindgender                       & factor  & Masc, Neut, Fem             \\
    Measure lemma  & Measureattraction                & numeric &                           \\
                   & (Measurecollo)                   & numeric &                           \\
                   & Measureclass                     & factor  & Physical, Container,      \\
                   &                                  &         & Amount, Portion, Rest     \\
                   & Measurefreq                      & numeric &                           \\
  \end{tabular}
  \caption{Annotated variables for the corpus studies}
  \label{tab:variables}
\end{table}

@@

To capture the influence of style mentioned in Section~\ref{sec:analyses}, two proxy variables were used.
At the document level, the DECOW14A corpus has an annotation for \textit{Badness}.
As described in \cite{SchaeferEa2013}, \textit{Badness} measures how well the distribution of highly frequent short words in the document matches a pre-generated language model for German.
They also show that the Badness score corresponds robustly with human raters' intuitions about text coherence and text quality (see the paper for an operationalisation of this notion).
Documents with higher Badness usually contain more incoherent language, shorter sentences, etc.
If the \PGCa\ actually favours more elaborate stylistic levels, a high \textit{Badness} should be correlated with fewer occurrences.
Documents in DECOW14 have also been annotated with a variable called \textit{Genitives}.
The higher the values of this variable, the lower the proportion of genitives among all case-bearing forms is.
A high number of genitives is also indicative of a more formal, elaborate style close to the written standard.
However, the use of this variable as a regressor in the present study might be considered problematic.
Since the \PGCa\ contains a genitive itself, the regressor variable \textit{Genitive} and the document-level variable \textit{Genitives} are not fully independent.
Since instances of the \PGCa\ make up for only a minute fraction of all genitives, however, I still use \textit{Genitives} as a regressor.

@@

The coefficient estimates are specified in Table~\ref{tab:smalltable} for each regressor (or regressor level) in the columns labelled \textit{Coefficient}.
Given the coding of the response variable, coefficients leaning to the positive side can be interpreted as characterising a configuration typical of the \PGCd.
For a robust quantification of the precision of the estimation, I ran a parametric bootstrap (using the \mbox{\textit{confint.merMod}} function from \textit{lme4}) with 1,000 replications and using the percentile method for the calculation of the intervals.
The resulting 95\% bootstrap confidence intervals are reported in Table~\ref{tab:smalltable} in the columns labelled \textit{CI low} and \textit{CI high} (= upper and lower 2.5th percentiles).
The column \textit{CI excludes 0} shows an asterisk for those intervals that do not include 0.
Furthermore, for each regressor, a p-value was obtained by dropping the regressor from the full model, re-estimating the nested model, and comparing it to the full model.
Instead of inexact Wald approximations and Likelihood Ratio Tests, I used a drop-in bootstrap replacement for the Likelihood Ratio Test in the form of the function \textit{PBmodcomp} from the \textit{pbkrtest} package \citep{HalekohHojsgaard2014}.
I call the corresponding value $p_{\text{PB}}$, and it is given in the respective columns in Table~\ref{tab:smalltable}.
Regressors which did not reach sig=0.05 in in the PBmodcomp test (\textit{Kindfreq}, \textit{Kindgender}, and \textit{Measurefreq}) were removed from the model, appear in brackets in Table~\ref{tab:smalltable}, and consequently have no coefficient estimates.
The overall intercept is -5.370 and represents \textit{Cardinal=Yes}, \textit{Measureclass=Physical} and 0 for all (z-transformed) numeric regressors.
The standard deviation in the random intercepts is 1.157 for \textit{Measurelemma} ($p_{\text{PB}}=0.001$) and 0.923 for \textit{Kindlemma} ($p_{\text{PB}}=0.002$).
Nakagawa \& Schielzeth's pseudo-coefficient of determination is $R_m^2=0.278$ and $R^2_c=0.566$ (see \citealp{Gries2015} for a basic introduction to these $R^2$ measures, or else \citealp{NakagawaSchielzeth2013}).

@@

For the main study, each of the 2,365 noun–noun combinations was queried in the alternating constructions \PGCa\ and \NACa\ in DECOW14A.%
\footnote{Due to efficiency problems with the old COW interface at the time, only ten slices of DECOW14A were used, which add up to approximately 10 billion tokens.}
For the manual annotation process, a random sub-sample was generated.
For each mass noun, the concordance was downsampled randomly to maximally 100 sentences, which resulted in 6,843 sentences without further downsampling.
In the manual annotation process the sample was further reduced to 5,063 sentences due to removal of noisy material, erroneous hits, and uninformative cases where the measure noun was in the genitive, in which case the \NACa\ cannot be distinguished from the \PGCa.
Given the careful sampling procedure described in this section and Section~\ref{sec:bootstrappinlemmapairs}, we can be highly certain that it contains all relevant and reasonably frequent noun–noun combinations in the target constructions.%
\footnote{In a similar fashion, the 100 most frequent measure nouns occurring with plural kind nouns were listed and queried, resulting in a sample of 871 sentences.
As stated in Section~\ref{sec:germanmeasurenps}, the \NACa\ is virtually never used with plural kind nouns, and this sample was not used except for quantifying the frequency of occurrence of the constructions (67 times \NACa\ and 794 times \PGCa).
The sample is distributed with the data package accompanying this paper.}

@@

Standard diagnostics show that the model quality is quite good.
Nakagawa \& Schielzeth's pseudo-coefficient of determination is $R_m^2=0.409$ and $R^2_c=0.495$.
The rate of correct predictions is 0.843, which means a proportional reduction of error of $\lambda=0.297$.
Generalised variance inflation factors for the regressors were calculated to check for multicollinearity \citep{FoxMonette1992,ZuurEa2010}, and the highest corrected $\text{GVIF}^{1/2\text{df}}$ was 1.520 for \textit{Cardinal}.
The lemma intercepts have standard deviations of $\sigma_{\text{Measurelemma}}=0.448$ and $\sigma_{\text{Kindlemma}}=0.604$.
Only \textit{Kindfreq} ($\mpPB=0.095$) could be seen as slightly too high to be convincing, failing at sig=0.05.

@@

The results reported in Section~\ref{sec:corpushierarchicalmodel} generally confirm the hypotheses from Section~\ref{sec:analyses}.
First, the prototypicality effect related to the non-alternating \PGCd\ and \NACb\ can be shown (see the effect plots in Figure~\ref{fig:eff:attraction}).%
\footnote{Effect plots were created using the \textit{effects} package \citep{Fox2003}.}
The effect is as expected:
if a lemma appears relatively more often in the \PGCd\ (compared to its frequency in the \NACb), the \PGCa\ tends to be chosen over the \NACa\ with this specific lemma.
The effect for measure nouns is stronger, and it was estimated with higher precision.

### 2018-04-08 Latex/sections/4experiments.tex
First round of shortening.

The first experiment tests preferences for constructions explicitly in a forced choice task.
% \cite{FordBresnan2013} use the \textit{split-100} task in which participants have to distribute 100 points between the alternatives, assigning more points to more natural sounding alternative.
% In essence, participants distribute a probability mass between two alternants, which is intended to produce more subtle results compared to a two-alternative forced-choice task such as in \cite{Rosenbach2013}, where participants have to choose one of two alternants.
% The split-100 paradigm has been criticised in \cite{ArppeJaervikivi2007}.
% The criticism was reiterated in \cite{DivjakEa2016}, where they use a forced-choice task.
% In \cite{VerhoevenTemme2017}, it was shown that results from forced-choice and split-100 experiments mostly converge (with some numeric intricacies related to the non-linear distribution of preferences for alternants).
% I present a forced-choice experiment in this section instead of a split-100 experiment not only because of some researchers' critical attitude towards the split-100 task, but also because in a dry run of the experiment, participants complained about the unnaturalness of distributing a probability mass across two alternants and tended to produce ratings of 0 or 100 (or 50, although to a lesser degree).
Participants had to choose between two sentences that differed only in that one contained the \NACa\, and the other one contained the \PGCa.
The analysis compares the probabilities assigned to the stimuli by the corpus-derived model with the frequency with which participants chose the alternants.
There were 24 participants (native speakers of German without reading or writing disabilities) aged 19 to 30 living permanently in [name of city redacted], who were recruited from introductory linguistics courses at [name of university redacted].
Although the experiment was conducted in the last four weeks of their first semester, participants had no deeper explicit knowledge of linguistics, grammar, or experimental methods.
None of them had ever participated in a forced-choice experiment before.
Participation was voluntary but participants received credit in partial fulfillment of course requirements.

>>>>

The first experiment tests preferences for constructions explicitly in a forced choice task.
Participants had to choose between two sentences that differed only in that one contained the \NACa\, and the other one contained the \PGCa.
The analysis compares the probabilities assigned to the stimuli by the corpus-derived model with the frequency with which participants chose the alternants.
There were 24 participants (native speakers of German without reading or writing disabilities) aged 19 to 30 living permanently in Berlin, who were recruited from introductory linguistics courses at Freie Universität Berlin.
Although the experiment was conducted in the last four weeks of their first semester, participants had no deeper explicit knowledge of linguistics, grammar, or experimental methods.
None of them had ever participated in a forced-choice experiment before.
Participation was voluntary but participants received credit in partial fulfillment of course requirements.

### 2018-04-08 Latex/sections/5conclusions.tex
First round of shortening.

Besides the methodological aspects mentioned above, future work could extend the validity of the results presented here through a more in-depth look at stylistic or register effects, for example using the new Biber-style annotations \citep{Biber1988} which will be released with a new version of the DECOW corpus soon.
Also, regional variation as a potentially influencing factor was already mentioned in Section~\ref{sec:prototypeeffects}.
As it would be infeasible to examine this with existing corpora, experimental work with participants from various regions might be the ideal approach.
A reviewer also pointed out that strongly lexicalised adjective-noun combinations like \textit{schwarzer Tee} `black tea' might have a tendency to occur in the \NACa\ because they have more compound-like qualities, blocking strong case inflection in between them.
While this potential effect was impossible to incorporate into the present study, it could be integrated into future research on the phenomenon.

>>>>

Besides the methodological aspects mentioned above, future work could extend the validity of the results presented here through a more in-depth look at stylistic or register effects, for example using the new Biber-style annotations \citep{Biber1988} which will be released with a new version of the DECOW corpus soon according to its creators.
Also, regional variation as a potentially influencing factor was already mentioned in Section~\ref{sec:prototypeeffects}.
As it would be infeasible to examine this with existing corpora, experimental work with participants from various regions might be the ideal approach.
A reviewer also pointed out that strongly lexicalised adjective-noun combinations like \textit{schwarzer Tee} `black tea' might have a tendency to occur in the \NACa\ because they have more compound-like qualities, blocking strong case inflection in between them.
While this potential effect was impossible to incorporate into the present study, it could be integrated into future research on the phenomenon.
